Maximum Entropy Spectral Analysis: a case study

### 2021-04-16 paper/mesa.tex
minor edits

As outlined in sec.~\ref{sec:Welch_comparison}, the MESA provides PSD estimates with less noise than the standard Welch algorithm, thus making it a good alternative for it. The use of MESA is particularly useful for short time series samples, where Welch method is outperformed in accuracy and conficence.
It has to be said that our method can be quite computationally expensive, as compared to standard Welch's algorithm. However, for short time series, the computational cost is still managable.

@@

We believe that Maximum Entropy Spectral Analysis, despite being an ``old" theory, has still the potential to become the standard in future time series analysis, due to its theorical elegance and to its reliable performance in a vast range of application.

>>>>

As outlined in sec.~\ref{sec:Welch_comparison}, the MESA provides PSD estimates with less noise than the standard Welch algorithm, thus making it a good alternative for it. The use of MESA is particularly useful for short time series samples, where Welch method is outperformed in accuracy and confidence.
It has to be said that our method can be quite computationally expensive, as compared to standard Welch's algorithm. However, for short time series, the computational cost is still managable.

@@

We believe that Maximum Entropy Spectral Analysis, despite being an ``old" theory, has still the potential to become the standard in future time series analysis, due to its theoretical elegance and to its reliable performance in a vast range of application.
